Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-01 prob.tex
prob.tex \appendix proving thm:analogTheorem21RichmanBridges1999

\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
is a approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\ket{\psi}\in S^{2}$, then the \emph{symmetrization} of $f$
with respect to $\ket{\psi}$ is the function~$g:S^{2}\rightarrow\mathbb{R}$
defined by
\[
g\left(\ket{\phi}\right)=f\left(\ket{\phi}\right)+f\left(\sigma\ket{\phi}\right)
\]
where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{\psi}$.\qed\end{definition}

@@

\begin{thm}\label{thm:analogCorollary22RichmanBridges1999}Let $f$
be an bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$m=\inf f$ or $m=\sup f$, and $W=\frac{W_{l}+W_{r}}{2}$. Let $Q$
be the quadratic form given by
\[
Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
\]
For each $\delta>0$, there is $\eta>0$ such that if
\begin{itemize}
\item $\ket{\psi}\in S^{2}$such that $\left|f\left(\ket{\psi}\right)-m\right|<\eta$,
and 
\item $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$.
\end{itemize}
then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\varDelta_{f}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
is the smallest integer not less than $x$.\qed\end{thm}

@@

\begin{cor}Let $f$ be a bounded continuous approximation frame function
of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{\psi}\right)$
or $m=\max f=f\left(\ket{\psi}\right)$, and $W=\frac{W_{l}+W_{r}}{2}$.
Let $Q$ be the quadratic form given by
\[
Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
\]
If $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$,
then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le3\left(W_{r}-W_{l}\right)$.\qed\end{cor}

@@

\begin{thm}Let $f$ be a bounded frame function on the unit sphere
in $\mathbb{R}^{3}$, and $\delta>0$. Then there is a quadratic form
$Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le3\delta$
for all $\ket{\phi}$ on the sphere.\qed\end{thm}

@@

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
of the symmetrization of $f$ with respect to $\ket{0}$ is at most
$2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$
for some integer $n\ge2\pi$. The exact $n$ could be computed to
minimize the oscillation when the function $f$ is given.\qed\end{lemma}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
Let $\ket{\phi}$ and $\ket{\phi'}$ be points in the northern hemisphere
with the same latitude~$\theta$. Let $a$ be the difference in longitudes
of $\ket{\phi}$ and $\ket{\phi'}$. Take $n$ steps along east-west
great circles to go from $\ket{\phi'}$ to a point $\ket{\phi_{s}}$
due south of $\ket{\phi}$. The difference in latitude between $\ket{\phi}$
and $\ket{\phi_{s}}$ is at most $\frac{a^{2}}{n}$, while, from (Lemma
16 to be typed),
\[
g\left(\ket{\phi_{s}}\right)\ge g\left(\ket{\phi'}\right)-n\left[2f\left(\ket{\psi}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
\]
When the difference in latitude between $\ket{\phi}$ and $\ket{\phi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\phi}$ and
$\ket{\phi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\phi}\right)\ge g\left(\ket{\phi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\phi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
Since $f$ is continuous in this case, we could solve $n\ge2\pi$
such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
\end{proof}
The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}
\begin{itemize}
\item Let $f$ be a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$, and 
\item $Q\left(\ket{\phi}\right)=W\left(1-\ip{0}{\phi}^{2}\right)$. 
\end{itemize}
Then, $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that 
\end{proof}

>>>>

\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
is a approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
then the \emph{symmetrization} of $f$ with respect to $\ket{0}$
is the function~$g:S^{2}\rightarrow\mathbb{R}$ defined by
\[
g\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\sigma\ket{\psi}\right)
\]
where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{0}$.\qed\end{definition}

@@

\begin{thm}\label{thm:analogCorollary22RichmanBridges1999}Let $f$
be an bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$m=\inf f$ or $m=\sup f$, and $W=\frac{W_{l}+W_{r}}{2}$. Let $Q$
be the quadratic form given by
\[
Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)
\]
For each $\delta>0$, there is $\eta>0$ such that if
\begin{itemize}
\item $\left|f\left(\ket{0}\right)-m\right|<\eta$, and 
\item $g$ is the symmetrization of $f$ with respect to $\ket{0}$.
\end{itemize}
then $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\varDelta_{f}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
is the smallest integer not less than $x$.\qed\end{thm}

@@

\begin{cor}Let $f$ be a bounded continuous approximation frame function
of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{0}\right)$
or $m=\max f=f\left(\ket{0}\right)$, and $W=\frac{W_{l}+W_{r}}{2}$.
Let $Q$ be the quadratic form given by
\[
Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)
\]
If $g$ is the symmetrization of $f$ with respect to $\ket{0}$,
then $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le3\left(W_{r}-W_{l}\right)$.\qed\end{cor}

@@

\begin{thm}Let $f$ be a bounded frame function on the unit sphere
in $\mathbb{R}^{3}$, and $\delta>0$. Then there is a quadratic form
$Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le3\delta$
for all $\ket{\psi}$ on the sphere.\qed\end{thm}

@@

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
of the symmetrization of $f$ with respect to $\ket{0}$ is at most
$\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
The exact $n$ could be computed to minimize the oscillation when
the function $f$ is given.\qed\end{lemma}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
with the same latitude~$\theta$. Let $a$ be the difference in longitudes
of $\ket{\psi}$ and $\ket{\psi'}$. Take $n$ steps along east-west
great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
due south of $\ket{\psi}$\footnote{Double check how many step at least from $\ket{\psi'}$ to a point
$\ket{\psi_{s}}$.}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be typed...},
\[
g\left(\ket{\psi_{s}}\right)\ge g\left(\ket{\psi'}\right)-n\left[2f\left(\ket{0}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
\]
When the difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\psi}$ and
$\ket{\psi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
Since $f$ is continuous in this case, we could solve $n\ge2\pi$
such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
\end{proof}
The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}
\begin{itemize}
\item Let $f$ be a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}\le\eta+g\left(\ket{\psi}\right)\le W_{r}$ for all
$\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.

If $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$ are
orthogonal vectors on the closed northern hemisphere, then $\ell\left(\ket{\psi_{0}}\right)+\ell\left(\ket{\psi_{1}}\right)+\ell\left(\ket{\psi_{2}}\right)=1$.
Conversely, if $a_{0}+a_{1}+a_{2}=1$, for $a_{i}\in\left[0,1\right]$,
then there exist orthogonal vectors~$\ket{\psi_{0}}$, $\ket{\psi_{1}}$,
and $\ket{\psi_{2}}$ on the closed northern hemisphere such that
$a_{i}=\ell\left(\ket{\psi_{i}}\right)$.

For any point $\ket{\psi}$ in the closed northern hemisphere, consider

For each $\varphi$ define $F_{\varphi}$ on $\left[0,1\right]$ by
setting $F_{\varphi}\left(\ell\left(\ket{\psi}\right)\right)=W-g\left(\ket{\psi}\right)$
where $\ket{\psi}$ is a point in the closed northern hemisphere with
longitude~$\varphi$. Then, $\left|F_{\varphi}\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|\le2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$
\end{proof}
